\tool: Revisiting BadUSB with Type-C

### 2021-03-19 WOOT/Files/experiment.tex
experiment revised

To further validate our attacking scenario, we conducted an experiment to simulate a real-world attack scenario. We selected 11 applications on  \mbox{\textit{HUAWEI P30 (ELE-AL00)}}, test each application with the following strategy
\ding{182} Attach \tool to the test device.
\ding{183} Login in with a test account.
\ding{184} Keep the default settings.
\ding{185} Simulate daily usage of the application.

During this experiment, we first tested full control mode which actively gathered sensitive information, then tested video capture mode which passively collected the sensitive information visited by victims. We noticed that, most sensitive information could be gathered directly through full control mode without victim's interaction, but there was also certain information that had to be collected passively through video capture mode. For example, as illustrated in Table~\ref{table:information_extracted}, in most applications, information like `Account' can be gathered directly while information like `Payment Password' cannot be collected until the victim inputs his/her password.

\subsubsection{Result}
In summary, as shown in Table~\ref{table:information_extracted}, our \tool is able to actively gather most sensitive information such as browsing history, personal account, phone number without victim's interaction. There also exists information such as payment password that is not available immediately, but such a piece of information can be collected once the victim input it on his/her smartphone. The gathered information can be further used to deduce victim's lock screen password and poses even greater threat to victim's privacy.

>>>>

\subsubsection{Experiment}

To further test the capabilities of \tool in this attack scenario, we conducted a simulation experiment.
We selected 11 applications on \mbox{\textit{HUAWEI P30 (ELE-AL00)}}, test each application with the following strategy
\ding{182} Login in with a test account.
\ding{183} Keep the default settings.
\ding{184} Attach attacker's \tool to the test device.
\ding{185} Simulate victim's daily usage of the application.

During this experiment, we tested full control mode which actively obtained sensitive information and video capture mode which passively obtained the sensitive information visited by the victim. We noticed that, most sensitive information could be obtained directly through full control mode without victim's interaction, but there was also certain information that had to be obtained passively through video capture mode. For example, as illustrated in Table~\ref{table:information_extracted}, in most applications, information like ``Account'' can be obtained directly while information like ``Payment Password'' cannot be obtained until the victim inputs his/her password.

\subsubsection{Result}
In summary, \tool is able to actively obtain most sensitive information from the screen, such as browsing history, personal account, phone number without victim's interaction. There also exists information such as payment password that is not available immediately, but such a piece of information can be obtained once the victim inputs it. The obtained information can be further used to guess the victim's lock screen password and poses even greater threat to victim's privacy.
